Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2020-12-07 analysis/paper/paper.Rmd
Reorder, clean up introduction

Modern plant pathological research has many facets given the array of disciplines and sub-disciplines currently involved.
Collectively, they contribute to increase our basic and applied knowledge on several aspects of pathogen biology and disease development to ultimately improve plant disease management.
Scientific research in the field varies from the purely observational or descriptive nature to inferential based on experimental or simulation-derived data sets.
Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available beyond what is reported in the scientific article and the ability of others to make use of your methods and results.
These research findings include biological materials (isolates or strains), nucleic/protein sequences, experimental and simulated raw data annotations, drawings and photographs and statistical analysis code among other materials and data generated as a course of conducting research.
That is, open science leads to reproducibility and replicability.

@@

## On Open Science and Reproducibility

Open science has become highlighted lately with many donors expecting data to be available [@government_of_canada_2016; @vannoorden2017; @ARC2018] and other scientists interested in sharing and collaborating more widely [@Wald2010].
While open science and reproducibility are not the same, they are linked.
By proactively practising open science, the work becomes more reproducible through the availability of data and code.

# Methods

>>>>

Modern plant pathological research has many facets given the array of disciplines and sub-disciplines currently involved.
Collectively, they contribute to increase our basic and applied knowledge of several aspects in pathogen biology and disease development to ultimately improve plant disease management.
Scientific research in the field varies from the purely observational or descriptive nature to inferential, based on experimental or simulation-derived data sets.
Whatever the case, research findings are verifiable based on how much of the research materials, processes and outcomes are made available beyond what is reported in the scientific article and the ability of others to make use of the methods and results.
These research findings include biological materials (isolates or strains), nucleic/protein sequences, experimental and simulated raw data annotations, drawings and photographs and statistical analysis code among other materials and data generated as a course of conducting research.

Recently, open science has been highlighted with many donors expecting data to be available [@government_of_canada_2016; @vannoorden2017; @ARC2018], journals in the field promoting the sharing of data [@TPP2020], and other scientists interested in sharing and collaborating more widely [@Wald2010].

While open science and reproducibility are not the same, they are linked.
By proactively practising open science, the work becomes more reproducible through the availability of data and code.
That is, open science leads to reproducibility and replicability.

@@

# Materials and methods
